### 2018-07-05 paper/3-abstractions.tex
Drop forward reference to profunctor optics

\noindent
Here \hs{c} stands for \emph{constraint}, such as \hs{Applicative} or \hs{Monad}.
A \hs{Task} describes a single build task, while \hs{Tasks} associates a
\hs{Task} to every non-input key; input keys are associated with
\hs{Nothing}. The highly-abstracted type\footnote{Readers
familiar with \emph{lenses} or \emph{profunctor optics} might recognise a
familiar pattern. We discuss this in~\S\ref{sec-related-optics}.} \hs{Task}
describes how to build a value when given a way to build its dependencies, and is
best explained by an example. Consider this \Excel spreadsheet:

>>>>

\noindent
Here \hs{c} stands for \emph{constraint}, such as \hs{Applicative} or \hs{Monad}.
A \hs{Task} describes a single build task, while \hs{Tasks} associates a
\hs{Task} to every non-input key; input keys are associated with \hs{Nothing}.
The highly-abstracted type \hs{Task} describes how to build a value when given
a way to build its dependencies, and is best explained by an example.
Consider this \Excel spreadsheet:
% \footnote{Readers familiar with \emph{lenses} or \emph{profunctor optics} might
% recognise a familiar pattern. We discuss this in~\S\ref{sec-related-optics}.}
